The \Prob

### 2013-03-07 bikes/bikes.tex
Finish bikes

The \prob~has far-reaching implications in many fields, including comestibility theory, deep-space navigation, maximum-jerk motion planning, and pop-math brainteasers.

@@

\newcommand\PA{\ensuremath{\mathtt{0}}}
\newcommand\PB{\ensuremath{\mathtt{1}}}
\newcommand\PC{\ensuremath{\mathtt{2}}}
\newcommand\PD{\ensuremath{\mathtt{3}}}
\newcommand\PE{\ensuremath{\mathtt{4}}}
\newcommand\distance[1]{\ensuremath{\mathsf{#1}}}
Formally we say that the {\em bicycle allocation} for this case is that person \PA~(the blue one, if you're reading this electronically or printed in color) rides bike $0$ for distances between $0$ and $1$, and person \PB~(the red one, if same) rides it for distances between $1$ and $2$. For short, we write:
\begin{eqnarray*}
	p_\PA &=& b_0@0 \\
	p_\PB &=& b_0@1
\end{eqnarray*}

@@

\newcommand\BA{\cellcolor{WildStrawberry}~\textcolor{White}{$b_0$}}
\newcommand\BB{\cellcolor{NavyBlue}      ~\textcolor{White}{$b_1$}}
\newcommand\BC{\cellcolor{OliveGreen}   ~\textcolor{White}{$b_2$}}
\newcommand\BD{\cellcolor{Dandelion}    ~\textcolor{White}{$b_3$}}
\newcommand\BE{\cellcolor{ProcessBlue}       ~\textcolor{White}{$b_3$}}
\begin{figure*}[t]
	\begin{subfigure}[b]{0.28\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|}
		& \multicolumn{2}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \\
		\cline{2-3}
		\multicolumn{1}{r|}{\PB} & & \BA \\
		\cline{2-3}
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\end{tabular}
		\caption{$2$ people, $1$ bike.}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{3}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \BB & \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PB} & & \BA & \BB \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PC} & \BB & & \BA \\
		\cline{2-4}
		\multicolumn{4}{c}{}\\
		\multicolumn{4}{c}{}\\
		\end{tabular}
		\caption{$3$ people, $2$ bikes.}
	\end{subfigure}
	\begin{subfigure}[b]{0.38\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{5}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} \\
		\hline
		\multicolumn{1}{r|}{\PA} &\BA&\BB&\BC&   & \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PB} &   &\BA&\BB&\BC& \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PC} &   &   &\BA&\BB&\BC\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PD} &\BC&   &   &\BA&\BB\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PE} &\BB&\BC&   &   &\BA\\
		\cline{2-6}
		\end{tabular}
		\caption{$5$ people, $3$ bikes.}
	\end{subfigure}
	\caption{Bicycle allocation policies for selected instances of the \prob. White cells represent walking; cells of different colours represent different bikes.
		Can you spot the French flag?}
	\label{fig:grids}
\end{figure*}

@@

\begin{theorem}[Contiguous Allocation]
For all $n$ and $k$, an optimal bicycle allocation exists in which no rider mounts and dismounts more than four times, and is given as follows:
\newcommand\open{\{}
\newcommand\close{\}}
\begin{center}
\begin{tabular}{rclll}
	$p_i$ & $=$ & $b_{(i~\mathsf{mod}~k)}@ \open i \rightsquigarrow i+k \close$ && $i \le n-k$ \\
	\\
	\multirow{2}{*}{$p_i$} & \multirow{2}{*}{$=$} & $b_{(i~\mathsf{mod}~k)}@ \open i\rightsquigarrow n \close,$ && \multirow{2}{*}{$i > n-k$} \\
	& & $b_{(i+k-n)}\hspace{0.5em}@ \open 0 \rightsquigarrow i+k-n \close$ \\
	\\
\end{tabular}
\end{center}
where $b_x@\open y\rightsquigarrow z\close$ expands to $b_x@(y)$, $b_x@(y+1)$, \dots $b_x@(z-1)$.

@@

%\begin{figure}[b]
%		\begin{center}
%			\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
%		& \multicolumn{6}{c}{distance} \\
%		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} \\
%		\hline
%		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&\BA&   &   \\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&\BB&   \\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC&\BC\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PD} &\BB&   &   &\BD&\BD&\BD\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PE} &\BC&\BC&   &   &\BA&\BA\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{fff} &\BD&\BD&\BD&   &   &\BB\\
%		\cline{2-7}
%		\end{tabular}
%		% 6/4
%			\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
%		& \multicolumn{6}{c}{distance} \\
%		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} \\
%		\hline
%		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&\BA&\BA&   \\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&\BB&\BB\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PC} &\BB&   &\BC&\BC&\BC&\BC\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PD} &\BC&\BC&   &\BD&\BD&\BD\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PE} &\BD&\BD&\BD&   &\BE&\BE\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{fff} &\BE&\BE&\BE&\BE&   &\BA\\
%		\cline{2-7}
%		\end{tabular}
%		% 7/3
%		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
%		& \multicolumn{7}{c}{distance} \\
%		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} & \multicolumn{1}{c|}{\distance{6}}\\
%		\hline
%		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&   &   &   &   \\
%		\cline{2-8}
%		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&   &   &   \\
%		\cline{2-8}
%		\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC&   &   \\
%		\cline{2-8}
%		\multicolumn{1}{r|}{\PD} &   &   &   &\BA&\BA&\BA&   \\
%		\cline{2-8}
%		\multicolumn{1}{r|}{\PE} &   &   &   &   &\BB&\BB&\BB\\
%		\cline{2-8}
%		\multicolumn{1}{r|}{fff} &\BB&   &   &   &   &\BC&\BC\\
%		\cline{2-8}
%		\multicolumn{1}{r|}{ggg} &\BC&\BC&   &   &   &   &\BA\\
%		\cline{2-8}
%		\end{tabular}
%		\end{center}
%		\caption{Scratch work}
%\end{figure}

@@

\initial{I}n Figure~\ref{fig:graph} we find our visualizings.
The horizontal line on top represents the state of the art, in which some participants walk the entire distance.
The bottom line represents the ideal case, in which there are enough bikes for everyone to ride together.

@@

\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem[Figueredo and Wolf, 2009]{Figueredo:2009dg}
Figueredo, A.~J. and Wolf, P. S.~A. (2009).
\newblock Assortative pairing and life history strategy - a cross-cultural
  study.
\newblock {\em Human Nature}, 20:317--330.

\end{thebibliography}

@@

>>>>

The \prob~has far-reaching implications in many fields, including comestibility theory~\cite{comestibility}, deep-space navigation~\cite{arkanoid}, maximum-jerk motion planning~\cite{jerk,jerk2}, and pop-math brainteasers.

@@

\newcommand\PA{\ensuremath{\mathtt{0}}}
\newcommand\PB{\ensuremath{\mathtt{1}}}
\newcommand\PC{\ensuremath{\mathtt{2}}}
\newcommand\PD{\ensuremath{\mathtt{3}}}
\newcommand\PE{\ensuremath{\mathtt{4}}}
\newcommand\PF{\ensuremath{\mathtt{5}}}
\newcommand\PG{\ensuremath{\mathtt{6}}}
\newcommand\distance[1]{\ensuremath{\mathsf{#1}}}
Formally we say that the {\em bicycle allocation} for this case is that person \PA~(the blue one, if you're reading this electronically or printed in color) rides bike $0$ for distances between $0$ and $1$, and person \PB~(the red one, if same) rides it for distances between $1$ and $2$. For short, we write:
\begin{eqnarray*}
	p_\PA &=& b_0@0 \\
	p_\PB &=& b_0@1
\end{eqnarray*}

@@

\newcommand\BA{\cellcolor{WildStrawberry}~\textcolor{White}{$b_0$}}
\newcommand\BB{\cellcolor{NavyBlue}      ~\textcolor{White}{$b_1$}}
\newcommand\BC{\cellcolor{OliveGreen}   ~\textcolor{White}{$b_2$}}
\newcommand\BD{\cellcolor{Dandelion}    ~\textcolor{White}{$b_3$}}
\newcommand\BE{\cellcolor{ProcessBlue}       ~\textcolor{White}{$b_4$}}
\begin{figure*}[t]
	\begin{subfigure}[b]{0.28\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|}
		& \multicolumn{2}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \\
		\cline{2-3}
		\multicolumn{1}{r|}{\PB} & & \BA \\
		\cline{2-3}
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\end{tabular}
		\caption{$2$ people, $1$ bike.}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{3}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \BB & \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PB} & & \BA & \BB \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PC} & \BB & & \BA \\
		\cline{2-4}
		\multicolumn{4}{c}{}\\
		\multicolumn{4}{c}{}\\
		\end{tabular}
		\caption{$3$ people, $2$ bikes.}
	\end{subfigure}
	\begin{subfigure}[b]{0.38\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{5}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} \\
		\hline
		\multicolumn{1}{r|}{\PA} &\BA&\BB&\BC&   & \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PB} &   &\BA&\BB&\BC& \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PC} &   &   &\BA&\BB&\BC\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PD} &\BC&   &   &\BA&\BB\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PE} &\BB&\BC&   &   &\BA\\
		\cline{2-6}
		\end{tabular}
		\caption{$5$ people, $3$ bikes.}
	\end{subfigure}
	\caption{Bicycle allocation policies for selected instances of the \prob. White cells represent walking; cells of different colours represent different bikes.
		Can you spot the French flag?}
	\label{fig:grids}
\end{figure*}

@@

\begin{theorem}[Contiguous Allocation]
\label{thm:cont}
For all $n$ and $k$, an optimal bicycle allocation exists in which no rider mounts and dismounts more than four times, and is given as follows:
\newcommand\open{\{}
\newcommand\close{\}}
\begin{center}
\begin{tabular}{rclll}
	$p_i$ & $=$ & $b_{(i~\mathsf{mod}~k)}@ \open i \rightsquigarrow i+k \close$ && $i \le n-k$ \\
	\\
	\multirow{2}{*}{$p_i$} & \multirow{2}{*}{$=$} & $b_{(i~\mathsf{mod}~k)}@ \open i\rightsquigarrow n \close,$ && \multirow{2}{*}{$i > n-k$} \\
	& & $b_{(i+k-n)}\hspace{0.5em}@ \open 0 \rightsquigarrow i+k-n \close$ \\
	\\
\end{tabular}
\end{center}
where $b_x@\open y\rightsquigarrow z\close$ expands to $b_x@(y)$, $b_x@(y+1)$, \dots $b_x@(z-1)$.

@@

@@

\initial{I}n Figure~\ref{fig:graph} we find our visualizings.
The horizontal line on top represents the previous state of the art, in which some participants walk the entire distance.
The bottom line represents the ideal case, in which there are enough bikes for everyone to ride together.

@@

\bibliographystyle{abbrv}
\bibliography{bikes}

@@

\newpage
\appendix
\section{Scratch Work}

These are some more tables we drew when deciding whether Theorem~\ref{thm:cont} was really true, and they were too colorful not to include.

\begin{figure}[h]
		\begin{center}
		%	\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		%& \multicolumn{6}{c}{distance} \\
		%person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} \\
		%\hline
		%\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&\BA&   &   \\
		%\cline{2-7}
		%\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&\BB&   \\
		%\cline{2-7}
		%\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC&\BC\\
		%\cline{2-7}
		%\multicolumn{1}{r|}{\PD} &\BB&   &   &\BD&\BD&\BD\\
		%\cline{2-7}
		%\multicolumn{1}{r|}{\PE} &\BC&\BC&   &   &\BA&\BA\\
		%\cline{2-7}
		%\multicolumn{1}{r|}{fff} &\BD&\BD&\BD&   &   &\BB\\
		%\cline{2-7}
		%\end{tabular}
		%% 6/4
		%	\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		%& \multicolumn{6}{c}{distance} \\
		%person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} \\
		%\hline
		%\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&\BA&\BA&   \\
		%\cline{2-7}
		%\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&\BB&\BB\\
		%\cline{2-7}
		%\multicolumn{1}{r|}{\PC} &\BB&   &\BC&\BC&\BC&\BC\\
		%\cline{2-7}
		%\multicolumn{1}{r|}{\PD} &\BC&\BC&   &\BD&\BD&\BD\\
		%\cline{2-7}
		%\multicolumn{1}{r|}{\PE} &\BD&\BD&\BD&   &\BE&\BE\\
		%\cline{2-7}
		%\multicolumn{1}{r|}{fff} &\BE&\BE&\BE&\BE&   &\BA\\
		%\cline{2-7}
		%\end{tabular}
		% 7/3
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
			& \multicolumn{7}{c}{distance} \\
			person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} & \multicolumn{1}{c|}{\distance{6}}\\
			\hline
			\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&   &   &   &   \\
			\cline{2-8}
			\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&   &   &   \\
			\cline{2-8}
			\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC&   &   \\
			\cline{2-8}
			\multicolumn{1}{r|}{\PD} &   &   &   &\BA&\BA&\BA&   \\
			\cline{2-8}
			\multicolumn{1}{r|}{\PE} &   &   &   &   &\BB&\BB&\BB\\
			\cline{2-8}
			\multicolumn{1}{r|}{\PF} &\BB&   &   &   &   &\BC&\BC\\
			\cline{2-8}
			\multicolumn{1}{r|}{\PG} &\BC&\BC&   &   &   &   &\BA\\
			\cline{2-8}
		\end{tabular}
		\vspace{1em}

		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
			& \multicolumn{7}{c}{distance} \\
			person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} & \multicolumn{1}{c|}{\distance{6}}\\
			\hline
			\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&\BA&\BA&   &   \\
			\cline{2-8}
			\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&\BB&\BB&   \\
			\cline{2-8}
			\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC&\BC&\BC\\
			\cline{2-8}
			\multicolumn{1}{r|}{\PD} &\BB&   &   &\BD&\BD&\BD&\BD\\
			\cline{2-8}
			\multicolumn{1}{r|}{\PE} &\BC&\BC&   &   &\BE&\BE&\BE\\
			\cline{2-8}
			\multicolumn{1}{r|}{\PF} &\BD&\BD&\BD&   &   &\BA&\BA\\
			\cline{2-8}
			\multicolumn{1}{r|}{\PG} &\BE&\BE&\BE&\BE&   &   &\BB\\
			\cline{2-8}
		\end{tabular}
		\end{center}
		\caption{
To those who printed in black-and-white and find these illegible, we say: stop reinforcing the color binary!}
\end{figure}
